%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{setspace}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {{\fontsize{70}{60}\selectfont \textbf{Govind Tomar}}} & Email : \href{mailto:govindtomar94@gmail.com}{\underline{govindtomar94@gmail.com}}\\
  {
  \href{https://www.linkedin.com/in/govind-tomar-557258194/}{\underline {LinkedIn}}
  { \(|\) }
  \href{https://github.com/404fixer}{\underline {Github}}
  } & Mobile : +91 9870663286 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology Sonepat (IIIT Sonepat)}{Sonepat, India}
      {Bachelor of Technology in Computer Science
}{Aug. 2019 -- Jul. 2023}
\begin{itemize}
\item CGPA : \textbf{8.74}/10.0
\end{itemize}

%     \resumeSubheading
%       {BDS International School}{Meerut, Uttar Pradesh}
%       {Schooling;}{Till March 2018}
  \resumeSubHeadingListEnd



 
 
 %-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \item{\textbf{\large }
  {\href{https://sync-m-coder.herokuapp.com/}{\textbf{{\large{\underline{\textbf{SyncM}}}}}}}
    {\href{https://github.com/404fixer/SyncM-Speaker}{{\lbrack{\underline{Github Link}}\rbrack}}}
    % \begin{itemize}
    %     \item {A Web Application using which you can play same music across different devices at the same time to boost the audio and have the experience of external speakers without actually having them.}
    %     \item {Built it using HTML, CSS, Javascript, on the frontend and NodeJS, expressJS, socket.io}
    % \end{itemize}
    
      {Build a Web App using which you can play same music across different devices at the same time to boost the audio and have the experience of external speakers without actually having them, along with a chatbox. Built it using socket.io (for real time, bidrectional event based communication), express and nodeJS.}
      }
   
   \item{{\href{http://sparsh-beauty-parlour.herokuapp.com/}{\underline{\textbf{Sparsh Beauty Parlour}}}}
    {\href{https://github.com/404fixer/sparsh-beauty-parlour}{\lbrack \underline{Github Link}\rbrack}
    }
    \linebreak
      {Designed and Developed a Web App for a Local Beauty Parlour to showcase their work and book an appointment using HTML, CSS, JavaScript, Bootstrap, nodeJS, and nodemailer (which allows to send emails from nodeJS).}
      }
    
    \item{\textbf{\large {RGB Colour Guessing Game}} {\href{https://github.com/404fixer/webDevLearningProject/tree/master/colorGameProject}{\lbrack \underline{Github Link}\rbrack}}
    \linebreak
      {Developed a game of guessing the colour (from the given visual colour options) by looking at the RGB code of it. Built it using HTML, CSS, and Vanilla JavaScript.}}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%https://www.overleaf.com/project/6123d683147b1428bedc547d
 

%-----------EXPERIENCE-----------------
\section{Achievements}
 \resumeSubHeadingListStart
     
     \item
     {Obtained Global Rank \textbf{518} in \textbf{Facebook Hacker Cup Qualification Round 2021}.} \href{https://drive.google.com/file/d/1jPu8BfnQKZ1c27xlJ-RbH9h47UY2SjvW/view?usp=sharing}{[\underline{Certificate Link}]} 
     \item {
        Obtained Global Rank\textbf{ 99} in \textbf{Codechef C.O.D.E.R.S. 2021}. \href{https://www.codechef.com/rankings/FOUR21B?order=asc&search=govindtomar21&sortBy=rank}{[\underline{Ranklist Link}]} 
     }
     \item {
        Obtained Global Rank\textbf{ 126} in \textbf{Codechef December Lunctime 2021}. \href{https://www.codechef.com/rankings/LTIME103B?order=asc&search=govindtomar21&sortBy=rank}{[\underline{Ranklist Link}]} 
     }
      \item {
        Obtained Global Rank\textbf{ 473} in \textbf{Codeforces Round #762 (Div. 3).} \href{https://codeforces.com/contest/1619/standings?list=da8ee0f7b6c9d6b336f1c30139f022f7}{[\underline{Standings Link}]} 
     }
     \item
     {Obtained Global Rank \textbf{1566} in \textbf{Google Kickstart Round E 2021}. (Username : 404fixer)}
  
   \item
     {Obtained Global Rank \textbf{2087} in \textbf{ICPC Amritapuri 2020 Preliminary Round}. (Team Name : global\_vars)}
     \item {
        Obtained\textbf{ 97.9999637} percentile in \textbf{JEE Main 2018} among a million candidates across the country.
     }
\resumeSubHeadingListEnd 


%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
% \item
{
{
     \textbf{Languages}{: C, C++, JavaScript, Java, Python }
    %  \hfill
   }
   \linebreak
   
    
%    \item
   
%    \item
   {
   \textbf{Developer Tools}{: Git, and Github}
   }
   \linebreak
%    \item
{
   \textbf{Operating Systems}{: MacOS, Windows, Ubuntu}
   }
   \linebreak

   {
   \textbf{Development}{: HTML, CSS, SASS, JavaScript, jQuery, express.js, mongoDB, Firebase, nodeJS, ReactJS}
   }
   \linebreak
   {
   \textbf{Miscellaneous}{: Front-end and Back-end Development, OOPS, OS, DBMS}
   }
   \linebreak
    {Experience working with \textbf{Web Applications}.
    %  \hfill
   }
   \linebreak
    {Proficient with \textbf{Data Structures And Algorithms} in C++.}
    %  \hfill
   }
 \resumeSubHeadingListEnd

 
%-----------Reach Out to me Here-----------------
\section{Coding Profiles}
 \resumeSubHeadingListStart
 \setstretch{.1}
   \item {
        {Codeforces handle : \href{https://codeforces.com/profile/govindtomar}{\textbf{\underline{govindtomar}}} (Maximum Rating : \textbf{1533 (Specialist)})}
     }
     \item {
        {Codechef handle : \href{https://www.codechef.com/users/govindtomar21}{\textbf{\underline{govindtomar21}}} (Maximum Rating : \textbf{2022 (5 Star Coder)}}
     }
     \item {
        {Atcoder handle : \href{https://atcoder.jp/users/404fixer}{\textbf{\underline{404fixer}}} (Maximum Rating : \textbf{892 (Green)})}
     }
\resumeSubHeadingListEnd 





%-------------------------------------------
\end{document}
